---
title: "Simple Simulation for Adaptive Transfer Lasso"
author: "Masaaki Takada"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    # toc_float: 
    #   collapsed: true
    #   smooth_scroll: true
---

#  Simulations

OLS vs Lasso vs Adaptive Lasso vs Transfer Lasso vs Adaptive Transfer Lasso

```{r, cache=FALSE, autodep=TRUE}
library(MASS)
library(Rcpp)
library(tidyverse)
library(trlasso)
library(plotly)
```

```{r, cache=TRUE, cache.lazy = FALSE, autodep=TRUE}
r <- 0.5
m_power <- 2
p <- 10
sigma <- 1

n_list <- c(500, 5000)
num <- 10

k <- 1
pf_max <- 1e12
pf_min <- 1e-12
pf_th <- 1e-12
gamma <- 1
gamma1 <- 1
gamma2 <- 1
eps <- 1e-8

log_n_lambda_list <- seq(from = -2, to = 2, by = 1/8)
log_n_eta_list <- seq(from = -2, to = 2, by = 1/8)
```

```{r, cache=TRUE, cache.lazy = FALSE, autodep=TRUE}
evaluate_beta <- function(beta_hat, beta, X_random, y_random, X_fixed, y_fixed, 
                          beta_tilde = 0) {
  nonzero <- (abs(beta) >= 1e-12)
  nonzero_hat <- (abs(beta_hat) >= 1e-12)
  invariant <- (abs(beta_hat - beta_tilde) < 1e-12)
  tibble(
    rmse_random = sqrt(mean((y_random - X_random %*% beta_hat)^2)),
    rmse_fixed = sqrt(mean((y_fixed - X_fixed %*% beta_hat)^2)),
    l2 = sqrt(sum((beta_hat - beta)^2)),
    sens = sum(nonzero_hat & nonzero) / max(sum(nonzero), 1),
    spec = sum((!nonzero_hat) & (!nonzero)) / max(sum(!nonzero), 1),
    ppv = sum(nonzero_hat & nonzero) / max(sum(nonzero_hat), 1),
    fval = 2 / ((1/sens) + (1/ppv)),
    acc = sum(nonzero_hat == nonzero) / length(nonzero),
    inv_acc = sum(nonzero & invariant) / sum(nonzero),
    num_nonzero = sum(nonzero_hat),
    num_invariant = sum(invariant)
    )
}
```

```{r, cache=TRUE, cache.lazy = FALSE, autodep=TRUE}
set.seed(0)

results <- tibble()

for (i in 1:num) {
  print(paste0("i = ", i))
  
  for (n in n_list) {
    res <- tibble()
    print(paste0("n = ", n))
    
    ###### data generation #####

    # coefficient
    beta <- c(c(3, 1.5, 0, 0, 2), rep(0, length=p-5))
    beta_source <- beta

    # data
    mu <- rep(0, length = p)
    Sigma <- matrix(0, nrow = p, ncol = p)
    for (j in 1:p) {
      for (k in 1:p) {
        Sigma[j, k] <- r^abs(j - k)
      }
    }
    
    # target data
    if (r == 0) {
      X <- matrix(rnorm(n = n * p, mean = 0, sd = 1), nrow = n, ncol = p)
    } else {
      X <- mvrnorm(n = n, mu = mu, Sigma = Sigma)
    }
    y <- X %*% beta + rnorm(n, mean = 0, sd = sigma)

    # source data
    m <- n^m_power
    if (r == 0) {
      X_source <- matrix(rnorm(n = m * p, mean = 0, sd = 1), 
                         nrow = m, ncol = p)
    } else {
      X_source <- mvrnorm(n = m, mu = mu, Sigma = Sigma)
    }
    y_source <- X_source %*% beta_source + rnorm(m, mean = 0, sd = sigma)
    
    # test data (same X as target)
    X_ts_fixed <- X
    y_ts_fixed <- X_ts_fixed %*% beta + rnorm(n, mean = 0, sd = sigma)
    
    # test data (different X from target)
    if (r == 0) {
      X_ts_random <- matrix(rnorm(n = n * p, mean = 0, sd = 1), 
                            nrow = n, ncol = p)
    } else {
      X_ts_random <- mvrnorm(n = n, mu = mu, Sigma = Sigma)
    }
    y_ts_random <- X_ts_random %*% beta + rnorm(n, mean = 0, sd = sigma)
    
    ###### modeling #####

    # ols with source data
    fit <- glm.fit(X_source, y_source)
    beta_ols_source <- fit$coefficients
    res <- res %>%
      bind_rows(tibble(
        method = "ols_source", 
        evaluate_beta(beta_ols_source, beta, 
                      X_ts_random, y_ts_random, X_ts_fixed, y_ts_fixed)
      ))

    # lasso
    for (log_n_lambda in log_n_lambda_list) {
      fit <- trlasso(X, y, lambda = k * n^log_n_lambda / n, eps = eps)
      beta_lasso <- fit$beta[, 1]
      res <- res %>%
        bind_rows(tibble(
          method = "lasso",
          log_n_lambda = log_n_lambda,
          evaluate_beta(beta_lasso, beta, 
                        X_ts_random, y_ts_random, X_ts_fixed, y_ts_fixed)
        ))
    }

    # adaptive lasso with ols
    for (log_n_lambda in log_n_lambda_list) {
      beta_tilde <- beta_ols_source
      pf_lasso <- sapply(1/abs(beta_tilde)^gamma, function(b){max(min(b, pf_max), pf_min)})
      fit <- trlasso(X, y, lambda = k * n^log_n_lambda / n, alpha = 1,
                     penalty.factor.lasso = pf_lasso,
                     penalty.factor.thresh = pf_th, eps = eps)
      beta_alasso <- fit$beta[, 1]
      res <- res %>%
        bind_rows(tibble(
          method = "alasso",
          log_n_lambda = log_n_lambda,
          evaluate_beta(beta_alasso, beta, 
                        X_ts_random, y_ts_random, X_ts_fixed, y_ts_fixed, beta_tilde)
        ))
    }

    # transfer lasso with ols
    for (log_n_lambda in log_n_lambda_list) {
      for (log_n_eta in log_n_eta_list) {
        beta_tilde <- beta_ols_source
        fit <- trlasso(X, y, 
                       lambda = k * (n^log_n_lambda + n^log_n_eta) / n, 
                       alpha = n^log_n_lambda / (n^log_n_lambda + n^log_n_eta),
                       beta_tilde = beta_tilde,
                       penalty.factor.thresh = pf_th, eps = eps)
        beta_trlasso <- fit$beta[, 1]
        res <- res %>%
          bind_rows(tibble(
            method = "trlasso",
            log_n_lambda = log_n_lambda,
            log_n_eta = log_n_eta,
            evaluate_beta(beta_trlasso, beta, 
                          X_ts_random, y_ts_random, X_ts_fixed, y_ts_fixed, beta_tilde)
          ))
      }
    }

    # adaptive transfer lasso with ols
    for (log_n_lambda in log_n_lambda_list) {
      for (log_n_eta in log_n_eta_list) {
        beta_tilde <- beta_ols_source
        pf_lasso <- sapply(1/abs(beta_tilde)^gamma1, function(b){max(min(b, pf_max), pf_min)})
        pf_trlasso <- sapply(abs(beta_tilde)^gamma2, function(b){max(min(b, pf_max), pf_min)})
        fit <- trlasso(X, y, 
                       lambda = k * (n^log_n_lambda + n^log_n_eta) / n, 
                       alpha = n^log_n_lambda / (n^log_n_lambda + n^log_n_eta),
                       beta_tilde = beta_tilde, 
                       penalty.factor.lasso = pf_lasso,
                       penalty.factor.trlasso = pf_trlasso,
                       penalty.factor.thresh = pf_th, eps = eps)
        beta_atrlasso <- fit$beta[, 1]
        res <- res %>%
          bind_rows(tibble(
            method = "atrlasso",
            log_n_lambda = log_n_lambda,
            log_n_eta = log_n_eta,
            evaluate_beta(beta_atrlasso, beta, 
                          X_ts_random, y_ts_random, X_ts_fixed, y_ts_fixed, beta_tilde)
          ))
      }
    }
    
    results <- results %>%
      bind_rows(tibble(
        res %>%
          dplyr::mutate(
            i = i,
            n = n,
            m = m,
            p = p,
            sigma = sigma
            )
        ))
  }
}
```

# Summary
```{r, cache=FALSE, autodep=TRUE}
results <- results %>%
  dplyr::mutate(method = factor(method, levels = c(
    "ols_source", "lasso_source",
    "ols", "lasso", "alasso", "trlasso", "atrlasso"
  )))

summary <- results %>%
  dplyr::select(-i) %>%
  dplyr::group_by(method, n, m, p, sigma, log_n_lambda, log_n_eta) %>%
  dplyr::summarise_all(list(mean = ~ mean(., na.rm = TRUE), se = ~ sd(., na.rm = TRUE) / sqrt(n())))

DT::datatable(summary)
```

# Trade-off Diagram for AdapTrLasso

## Convergence Rate

```{r, cache=FALSE, autodep=TRUE, fig.width=7, fig.height=4, dpi=200}
summary %>%
  filter(method == "atrlasso") %>%
  group_by(log_n_lambda, log_n_eta) %>%
  summarise(convergence_rate = -(log10(l2_mean[which.max(n)]) - log10(l2_mean[which.min(n)])) / (log10(max(n)) - log10(min(n))), .groups = "keep") %>%
  ggplot(aes(x = log_n_eta, y = log_n_lambda, fill = convergence_rate)) +
  geom_tile() +
  scale_fill_gradient2(limits = c(-1, 1.1), midpoint = 0, oob = ~ scales::squish(., range = c(-1, 1.1))) +
  scale_x_continuous(breaks = seq(-2, 2, 1/2)) +
  scale_y_continuous(breaks = seq(-2, 2, 1/2)) +
  geom_segment(aes(x = -2-1/16, y = 0.5, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 0.5, y = 0.5, xend = 2+1/16, yend = 2+1/16), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -2-1/16, y = 1, xend = 1, yend = 1), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 0.5, y = -2-1/16, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 1.5, y = -2-1/16, xend = 1.5, yend = -0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -2-1/16, y = -0.5, xend = 1.5, yend = -0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 1.5, y = -0.5, xend = 2+1/16, yend = 0+1/16), 
               linetype = "dashed", color = "gray40") +
  theme(text = element_text(size = 15)) + 
  coord_fixed()
```

## Active Variable Selection Consistency

```{r, cache=FALSE, autodep=TRUE, fig.width=7, fig.height=4, dpi=200}
summary %>%
  filter(method == "atrlasso") %>%
  group_by(log_n_lambda, log_n_eta) %>%
  summarise(active_selection_ratio = acc_mean[which.max(n)], .groups = "keep") %>%
  ggplot(aes(x = log_n_eta, y = log_n_lambda, fill = active_selection_ratio)) +
  geom_tile() +
  scale_fill_continuous(limits = c(0, 1.1), high = "#132B43", low = "#56B1F7") +
  scale_x_continuous(breaks = seq(-2, 2, 1/2)) +
  scale_y_continuous(breaks = seq(-2, 2, 1/2)) +
  geom_segment(aes(x = -2-1/16, y = 0.5, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 0.5, y = 0.5, xend = 2+1/16, yend = 2+1/16), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -2-1/16, y = 1, xend = 1, yend = 1), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 0.5, y = -2-1/16, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 1.5, y = -2-1/16, xend = 1.5, yend = -0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -2-1/16, y = -0.5, xend = 1.5, yend = -0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 1.5, y = -0.5, xend = 2+1/16, yend = 0+1/16), 
               linetype = "dashed", color = "gray40") +
  theme(text = element_text(size = 15)) + 
  coord_fixed()
```


## Invariant Variable Selection Consistency

```{r, cache=FALSE, autodep=TRUE, fig.width=7, fig.height=4, dpi=200}
summary %>%
  filter(method == "atrlasso") %>%
  group_by(log_n_lambda, log_n_eta) %>%
  summarise(invariant_selection_ratio = inv_acc_mean[which.max(n)], .groups = "keep") %>%
  ggplot(aes(x = log_n_eta, y = log_n_lambda, fill = invariant_selection_ratio)) +
  geom_tile() +
  scale_fill_continuous(limits = c(0, 1.1), high = "#132B43", low = "#56B1F7") +
  scale_x_continuous(breaks = seq(-2, 2, 1/2)) +
  scale_y_continuous(breaks = seq(-2, 2, 1/2)) +
  geom_segment(aes(x = -2-1/16, y = 0.5, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 0.5, y = 0.5, xend = 2+1/16, yend = 2+1/16), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -2-1/16, y = 1, xend = 1, yend = 1), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 0.5, y = -2-1/16, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 1.5, y = -2-1/16, xend = 1.5, yend = -0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -2-1/16, y = -0.5, xend = 1.5, yend = -0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 1.5, y = -0.5, xend = 2+1/16, yend = 0+1/16), 
               linetype = "dashed", color = "gray40") +
  theme(text = element_text(size = 15)) + 
  coord_fixed()
```


# Trade-off Diagram for TrLasso

## Convergence Rate

```{r, cache=FALSE, autodep=TRUE, fig.width=7, fig.height=4, dpi=200}
summary %>%
  filter(method == "trlasso") %>%
  group_by(log_n_lambda, log_n_eta) %>%
  summarise(convergence_rate = -(log10(l2_mean[which.max(n)]) - log10(l2_mean[which.min(n)])) / (log10(max(n)) - log10(min(n))), .groups = "keep") %>%
  ggplot(aes(x = log_n_eta, y = log_n_lambda, fill = convergence_rate)) +
  geom_tile() +
  scale_fill_gradient2(limits = c(-1, 1.1), midpoint = 0, oob = ~ scales::squish(., range = c(-1, 1.1))) +
  scale_x_continuous(breaks = seq(-2, 2, 1/2)) +
  scale_y_continuous(breaks = seq(-2, 2, 1/2)) +
  geom_segment(aes(x = -2-1/16, y = 0.5, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -2-1/16, y = 1, xend = 1, yend = 1), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 0.5, y = 0.5, xend = 2+1/16, yend = 2+1/16), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 0.5, y = -2-1/16, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  theme(text = element_text(size = 15)) + 
  coord_fixed()
```

## Active Variable Selection Consistency

```{r, cache=FALSE, autodep=TRUE, fig.width=7, fig.height=4, dpi=200}
summary %>%
  filter(method == "trlasso") %>%
  group_by(log_n_lambda, log_n_eta) %>%
  summarise(active_selection_ratio = acc_mean[which.max(n)], .groups = "keep") %>%
  ggplot(aes(x = log_n_eta, y = log_n_lambda, fill = active_selection_ratio)) +
  geom_tile() +
  scale_fill_continuous(limits = c(0, 1.1), high = "#132B43", low = "#56B1F7") +
  scale_x_continuous(breaks = seq(-2, 2, 1/2)) +
  scale_y_continuous(breaks = seq(-2, 2, 1/2)) +
  geom_segment(aes(x = -2-1/16, y = 0.5, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -2-1/16, y = 1, xend = 1, yend = 1), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 0.5, y = 0.5, xend = 2+1/16, yend = 2+1/16), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 0.5, y = -2-1/16, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  theme(text = element_text(size = 15)) + 
  coord_fixed()
```


## Invariant Variable Selection Consistency

```{r, cache=FALSE, autodep=TRUE, fig.width=7, fig.height=4, dpi=200}
summary %>%
  filter(method == "trlasso") %>%
  group_by(log_n_lambda, log_n_eta) %>%
  summarise(invariant_selection_ratio = inv_acc_mean[which.max(n)], .groups = "keep") %>%
  ggplot(aes(x = log_n_eta, y = log_n_lambda, fill = invariant_selection_ratio)) +
  geom_tile() +
  scale_fill_continuous(limits = c(0, 1.1), high = "#132B43", low = "#56B1F7") +
  scale_x_continuous(breaks = seq(-2, 2, 1/2)) +
  scale_y_continuous(breaks = seq(-2, 2, 1/2)) +
  geom_segment(aes(x = -2-1/16, y = 0.5, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -2-1/16, y = 1, xend = 1, yend = 1), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 0.5, y = 0.5, xend = 2+1/16, yend = 2+1/16), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = 0.5, y = -2-1/16, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  theme(text = element_text(size = 15)) + 
  coord_fixed()
```

# Trade-off Diagram for AdaptLasso

## Convergence Rate

```{r, cache=FALSE, autodep=TRUE, fig.width=7, fig.height=4, dpi=200}
summary %>%
  filter(method == "alasso") %>%
  group_by(log_n_lambda) %>%
  summarise(convergence_rate = -(log10(l2_mean[which.max(n)]) - log10(l2_mean[which.min(n)])) / (log10(max(n)) - log10(min(n))), .groups = "keep") %>%
  ggplot(aes(x = 0, y = log_n_lambda, fill = convergence_rate)) +
  geom_tile() +
  scale_y_continuous(breaks = seq(-2, 2, 1/2)) +
  scale_fill_gradient2(limits = c(-1, 1.1), midpoint = 0, oob = ~ scales::squish(., range = c(-1, 1.1))) +
  geom_segment(aes(x = -0.5, y = 1, xend = 0.5, yend = 1), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -0.5, y = 0.5, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -0.5, y = 0.5-m_power/2, xend = 0.5, yend = 0.5-m_power/2), 
               linetype = "dashed", color = "gray40") +
  theme(text = element_text(size = 15)) + 
  coord_fixed()
```

## Active Variable Selection Consistency

```{r, cache=FALSE, autodep=TRUE, fig.width=7, fig.height=4, dpi=200}
summary %>%
  filter(method == "alasso") %>%
  group_by(log_n_lambda) %>%
  summarise(active_selection_ratio = acc_mean[which.max(n)], .groups = "keep") %>%
  ggplot(aes(x = 0, y = log_n_lambda, fill = active_selection_ratio)) +
  geom_tile() +
  scale_fill_continuous(limits = c(0, 1.1), high = "#132B43", low = "#56B1F7") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  geom_segment(aes(x = -0.5, y = 1, xend = 0.5, yend = 1), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -0.5, y = 0.5, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -0.5, y = 0.5-m_power/2, xend = 0.5, yend = 0.5-m_power/2), 
               linetype = "dashed", color = "gray40") +
  theme(text = element_text(size = 15)) + 
  coord_fixed()
```


## Invariant Variable Selection Consistency

```{r, cache=FALSE, autodep=TRUE, fig.width=7, fig.height=4, dpi=200}
summary %>%
  filter(method == "alasso") %>%
  group_by(log_n_lambda) %>%
  summarise(invariant_selection_ratio = inv_acc_mean[which.max(n)], .groups = "keep") %>%
  ggplot(aes(x = 0, y = log_n_lambda, fill = invariant_selection_ratio)) +
  geom_tile() +
  scale_y_continuous(breaks = seq(-2, 2, 1/2)) +
  scale_fill_continuous(limits = c(0, 1.1), high = "#132B43", low = "#56B1F7") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  geom_segment(aes(x = -0.5, y = 1, xend = 0.5, yend = 1), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -0.5, y = 0.5, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -0.5, y = 0.5-m_power/2, xend = 0.5, yend = 0.5-m_power/2), 
               linetype = "dashed", color = "gray40") +
  theme(text = element_text(size = 15)) + 
  coord_fixed()
```


# Trade-off Diagram for Lasso

## Convergence Rate

```{r, cache=FALSE, autodep=TRUE, fig.width=7, fig.height=4, dpi=200}
summary %>%
  filter(method == "lasso") %>%
  group_by(log_n_lambda) %>%
  summarise(convergence_rate = -(log10(l2_mean[which.max(n)]) - log10(l2_mean[which.min(n)])) / (log10(max(n)) - log10(min(n))), .groups = "keep") %>%
  ggplot(aes(x = 0, y = log_n_lambda, fill = convergence_rate)) +
  geom_tile() +
  scale_y_continuous(breaks = seq(-2, 2, 1/2)) +
  scale_fill_gradient2(limits = c(-1, 1.1), midpoint = 0, oob = ~ scales::squish(., range = c(-1, 1.1))) +
  geom_segment(aes(x = -0.5, y = 1, xend = 0.5, yend = 1), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -0.5, y = 0.5, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  theme(text = element_text(size = 15)) + 
  coord_fixed()
```

## Active Variable Selection Consistency

```{r, cache=FALSE, autodep=TRUE, fig.width=7, fig.height=4, dpi=200}
summary %>%
  filter(method == "lasso") %>%
  group_by(log_n_lambda) %>%
  summarise(active_selection_ratio = acc_mean[which.max(n)], .groups = "keep") %>%
  ggplot(aes(x = 0, y = log_n_lambda, fill = active_selection_ratio)) +
  geom_tile() +
  scale_y_continuous(breaks = seq(-2, 2, 1/2)) +
  scale_fill_continuous(limits = c(0, 1.1), high = "#132B43", low = "#56B1F7") +
  geom_segment(aes(x = -0.5, y = 1, xend = 0.5, yend = 1), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -0.5, y = 0.5, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  theme(text = element_text(size = 15)) + 
  coord_fixed()
```


## Invariant Variable Selection Consistency

```{r, cache=FALSE, autodep=TRUE, fig.width=7, fig.height=4, dpi=200}
summary %>%
  filter(method == "lasso") %>%
  group_by(log_n_lambda) %>%
  summarise(invariant_selection_ratio = inv_acc_mean[which.max(n)], .groups = "keep") %>%
  ggplot(aes(x = 0, y = log_n_lambda, fill = invariant_selection_ratio)) +
  geom_tile() +
  scale_y_continuous(breaks = seq(-2, 2, 1/2)) +
  scale_fill_continuous(limits = c(0, 1.1), high = "#132B43", low = "#56B1F7") +
  geom_segment(aes(x = -0.5, y = 1, xend = 0.5, yend = 1), 
               linetype = "dashed", color = "gray40") +
  geom_segment(aes(x = -0.5, y = 0.5, xend = 0.5, yend = 0.5), 
               linetype = "dashed", color = "gray40") +
  theme(text = element_text(size = 15)) + 
  coord_fixed()
```
